% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

\documentclass[11pt]{article}

% Remove the "review" option to generate the final version.
% \usepackage[review]{MAIN}
\usepackage[]{MAIN}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}

% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary, and may be commented out.
% However, it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% This is also not strictly necessary, and may be commented out.
% However, it will improve the aesthetics of text in
% the typewriter font.
\usepackage{inconsolata}


% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

\title{Community Detection and Analysis on DBLP v9 Dataset: Centrality, Network Metrics, and Predictive Modeling}

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{
%   Author 1 \and ... \and Author n \\
%   Address line \\ ... \\ Address line
% }
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
\author{
  Xiang Zheng \\ 21307110169 \And  
  ... 
  \vspace{0.7cm} \\ % Add some space before the school name
  \hfill School of Data Science, Fudan University \hfill
  \And
  Author n \\ Address line
}

\begin{document}
\maketitle
\begin{abstract}
	abstract
\end{abstract}

\section{Introduction}

Network analysis has become an essential methodology for investigating complex systems across diverse domains. The \href{https://www.aminer.cn/citation}{DBLP dataset}, a comprehensive bibliographic repository of computer science publications, provides a rich foundation for exploring collaboration patterns and scholarly relationships. This project employs advanced graph analysis techniques to uncover the structural and functional properties of the DBLP v9 dataset.

The study is organized into five core components, each addressing a key aspect of network analysis:

\begin{itemize}
	\item \textbf{Preprocessing}: The raw DBLP dataset was transformed into a structured network by performing data cleaning, filtering, and splitting. Key preprocessing steps included handling missing data, defining nodes and edges, and attributing properties to network elements to prepare the dataset for analysis.
	\item \textbf{Community Detection}: Cohesive subgroups within the network were identified using algorithms such as Louvain, Label Propagation, and Multi-level. These communities reveal collaborative dynamics, research specializations, and the structural foundations of scholarly interactions.
	\item \textbf{Centrality Analysis}: Degree centrality and PageRank centrality were employed to identify influential nodes, revealing hubs and authoritative figures within the network. Additional metrics, including community diameters and average citations per author, were analyzed to characterize structural and functional network properties. The degree distribution was assessed to evaluate the network's topology, with visual representations provided in the visualization section.
	\item \textbf{Link Prediction}: The GLACE model was employed on the Cora-ML dataset, a citation network of machine learning research papers, to predict potential future connections between nodes. Structural features such as common neighbors and Jaccard similarity served as input, with the model’s performance assessed using metrics like AUC and AP. This analysis offers insights into evolving citation patterns and the dynamics of scholarly connectivity.
	\item \textbf{Visualization System}: An intuitive visualization system was developed to facilitate the interpretation of results. Built using \textbf{Python} for the core implementation and \textbf{D3.js} for dynamic and interactive visualization, the system presents community structures, central nodes, and network statistics through graphical representations. This approach offers a comprehensive and visually accessible overview of the network's topology and dynamics.
\end{itemize}

By integrating these analytical components, this study aims to elucidate the structural characteristics, key actors, and potential evolution of the DBLP co-authorship and publication network. The methodologies and findings presented contribute to a deeper understanding of scholarly collaboration patterns and academic network dynamics.



\section{Preprocessing}

The preprocessing phase plays a crucial role in transforming the raw DBLP v9 dataset into a structured format suitable for comprehensive analysis. This stage encompasses data cleaning, network construction, and feature engineering. The DBLP v9 dataset was selected due to its balance between computational efficiency and the level of detail required to explore academic collaboration dynamics. Moreover, its extensive coverage of computer science literature ensures the robustness of the analysis.

\subsection{Dataset Selection}

The DBLP-Citation-network V9 dataset was selected based on several factors, as shown in Table \ref{tab:dblp_citation_networks}. While earlier versions provide valuable data, V9 was preferred due to its balance between data richness and computational manageability, making it well-suited for the available resources.

\begin{table*}[h!] 
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline
		\textbf{Data Set}         & \textbf{\# Papers} & \textbf{\# Citation Relationships} & \textbf{Comment}           \\
		\hline
		Citation-network V1       & 629,814            & >632,752                           &                            \\
		Citation-network V2       & 1,397,240          & >3,021,489                         &                            \\
		DBLP-Citation-network V3  & 1,632,442          & >2,327,450                         &                            \\
		DBLP-Citation-network V4  & 1,511,035          & 2,084,019                          & Arnetminer [2011-01-08]    \\
		DBLP-Citation-network V5  & 1,572,277          & 2,084,019                          & Arnetminer [2011-02-21]    \\
		DBLP-Citation-network V6  & 2,084,055          & 2,244,018                          & Arnetminer [2013-09-29]    \\
		DBLP-Citation-network V7  & 2,244,021          & 4,354,534                          & Arnetminer [2014-05-25]    \\
		DBLP-Citation-network V8  & 3,272,991          & 8,466,859                          & Arnetminer [2016-07-14]    \\
		ACM-Citation-network V8   & 2,381,688          & 10,476,564                         & Arnetminer [2016-04-02]    \\
		ACM-Citation-network V9   & 2,385,022          & 9,671,893                          & Arnetminer [2017-01-20]    \\
		DBLP-Citation-network V9  & 3,680,007          & 1,876,067                          & Arnetminer [2017-07-03]    \\
		DBLP-Citation-network V10 & 3,079,007          & 25,166,994                         &                            \\
		DBLP-Citation-network V11 & 4,107,340          & 36,624,464                         & OAG [2019-05-05]           \\
		DBLP-Citation-network V12 & 4,894,081          & 45,564,149                         & DBLP+Citation [2020-04-09] \\
		DBLP-Citation-network V13 & 5,354,309          & 48,227,950                         & DBLP+Citation [2021-05-14] \\
		DBLP-Citation-network V14 & 5,259,858          & 36,630,661                         & DBLP+Citation [2023-01-31] \\
		\hline
	\end{tabular}
	\caption{Summary of DBLP Citation Networks Versions}
	\label{tab:dblp_citation_networks}
\end{table*}

DBLP-Citation-network V9 was chosen for the following reasons:

\begin{itemize}
	\item \textbf{Data Completeness:} V9 includes 3,680,007 papers and 1,876,067 citation relationships, offering a comprehensive yet manageable dataset.
	\item \textbf{Timeliness:} Released on July 3, 2017, V9 reflects current citation trends up to that point.
	\item \textbf{Balanced Size:} Compared to later versions, V9 offers a good balance between data volume and computational feasibility.
	\item \textbf{Sufficient Coverage:} V9’s size enables a wide-ranging analysis of academic collaborations and citation patterns.
\end{itemize}

Thus, DBLP-Citation-network V9 was selected for its balance of data richness and computational efficiency, making it ideal for this study.


\subsection{Data Cleaning and Integration}

The raw dataset contains metadata, including titles, authors, venues, and citations. The initial cleaning process involved grouping records by paper, addressing missing or inconsistent data, and resolving redundancies. Missing fields, such as titles, authors, and venues, were assigned default values to ensure consistency, preparing the dataset for subsequent analysis.

\subsection{Network Construction}

The dataset was structured as a bipartite graph, where authors are represented as nodes and co-authorships as edges. Attributes such as publication count and co-authorship frequency were assigned to the nodes and edges, respectively. Additionally, citation relationships were extracted to construct a directed citation network. This dual representation of collaboration and citation dynamics allows for a comprehensive analysis of academic interactions.

\subsection{Feature Engineering}

To enhance the analytical power of the dataset, several key features were engineered:

\begin{itemize}
	\item \textbf{Co-authorship Mapping:} Authors were assigned unique identifiers, and co-authorship relationships were mapped, with edge weights representing the frequency of collaboration.
	\item \textbf{Citation Analysis:} Citation relationships were used to calculate in-degree (citations received) and out-degree (citations made) for each paper, providing insights into the influence and impact of academic works.
	\item \textbf{Venue Indexing:} Publication venues were indexed to ensure uniform representation across the dataset, enabling venue-specific analyses.
\end{itemize}

\subsection{Dataset Filtering}

To improve computational efficiency, papers with no citations and references were flagged as isolates and excluded from the analysis. Furthermore, thresholds were applied to prioritize significant relationships, ensuring that only meaningful data were retained for the analysis.



\section{Community Mining}

\section{Centrality Measurement}

\section{Link Prediction}

\section{Visualization System}

\section{Conclusion}

\section*{Acknowledgements}


% % Entries for the entire Anthology, followed by custom entries
% \bibliography{anthology,custom}
% \bibliographystyle{acl_natbib}

% \appendix

% \section{Example Appendix}
% \label{sec:appendix}

% This is a section in the appendix.

\end{document}
